### 2020-07-02 evaluation.tex
table 1

\begin{figure}[!t]
    \centering
    \subfigure[Traditional Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
    \subfigure[Optical Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
    \hfill
    \caption{Performance in Random Environment using Traditional Lens and Optical Lens.}
    \label{fig:control}
\end{figure}

@@

\subsection{Performance with fewer available images}
\begin{figure}[!t]
    \centering
    \subfigure[Traditional Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
    \subfigure[Optical Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
    \hfill
    \caption{Performance with fewer available images using Traditional Lens and Optical Lens.}
    \label{fig:number}
\end{figure}
As mentioned in sec.~\ref{sec-design}, our model is designed to work on any number of input images, the only limitation being that these images are snapshots of the same scene. This design is requisite because in certain scenarios the data displayed on the victim's screen is transient and ever-changing, e.g. password entry, where only the last character of the password is visible. We evaluated the impact of fewer available images to the performance of the SR model. The results are shown in fig.~\ref{fig:number}. We tested at the 1.8m daytime scenario for traditional lens and 6m daytime scenario for optical lens.

@@

\begin{figure}[!t]
    \centering
    \subfigure[Traditional Lens]{\includegraphics[width=0.36\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
    \subfigure{\includegraphics[width=0.36\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
    \hfill
    \caption[Optical Lens]{Performance for Adapting Ability using Traditional Lens and Optical Lens.}
    \label{fig:adapting}
\end{figure}

>>>>

\begin{figure}[!t]
    \centering
    \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_2.pdf}\label{fig-random-1}}
    \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_2_2.pdf}\label{fig-random-2}}
    \hfill
    \caption{Performance in Random Environment using Traditional Lens and Optical Lens.}
    \label{fig:control}
\end{figure}

@@

\subsection{Performance with fewer available images}
\begin{figure}[!t]
    \centering
    \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_5.pdf}\label{fig-image-tranditional-2}}
    \subfigure[Optical Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_6.pdf}\label{fig-image-optical-2}}
    \hfill
    \caption{Performance with fewer available images using Traditional Lens and Optical Lens.}
    \label{fig:number}
\end{figure}
As mentioned in sec.~\ref{sec-design}, our model is designed to work on any number of input images, the only limitation being that these images are snapshots of the same scene. This design is requisite because in certain scenarios the data displayed on the victim's screen is transient and ever-changing, e.g. password entry, where only the last character of the password is visible. We evaluated the impact of fewer available images to the performance of the SR model. The results are shown in fig.~\ref{fig:number}. We tested at the 1.8m daytime scenario for traditional lens and 6m daytime scenario for optical lens.

@@

\begin{figure}[!t]
    \centering
    \subfigure[Traditional Lens]{\includegraphics[width=0.40\textwidth]{./pic/data_3.pdf}\label{fig-adapt-tranditional}}
    \subfigure{\includegraphics[width=0.40\textwidth]{./pic/data_4.pdf}\label{fig-adapt-optical}}
    \hfill
    \caption[Optical Lens]{Performance for Adapting Ability using Traditional Lens and Optical Lens.}
    \label{fig:adapting}
\end{figure}

### 2020-07-02 related_work.tex
table 1

\section{Related Work}
\label{sec-related-work}
\begin{table}[t]
  \caption{A comparison of the state-of-the-arts on shoulder surfing.}
  \vspace{2mm}
  \begin{center}
  \begin{tabular}{cccc}
  \hline
   Reference & Scenarios & Training & distance$^{\mathrm{a}}$ \\
  \hline
  Eiband et al.~\cite{eiband2017understanding}  & naked eye & trained & 1 meter \\
  Kwon et al.~\cite{kwon2013covert}  & naked eye & untrained  & Intimate$^{\mathrm{b}}$\\
Schaub et al.~\cite{schaub2012password} & naked eye & untrained & Intimate\\
  Maggi et al.~\cite{maggi2011poster}  & camera & untrained  & Intimate \\
  \hline
  \hline
  \textbf{\textsf{SRPeek}} & COTS phones & trained  & 1.8 / 6 meter\\
  \hline
  \multicolumn{4}{l}{$^{\mathrm{a}}$The maximum distance to the victim's screen.}\\

  \multicolumn{4}{l}{$^{\mathrm{b}}$The attacker stands next to or behind the victim.}\\
  \end{tabular}
  \label{tbl:comparison}
  \end{center}
\end{table}

>>>>

\section{Related Work}
\label{sec-related-work}
\begin{table}[t]
  \caption{A comparison of the state-of-the-arts on shoulder surfing.}
  \vspace{2mm}
  \begin{center}
  \begin{tabular}{ccccc}
  \hline
   Reference & Scenarios   & Metric & \begin{tabular}[c]{@{}l@{}}Quantitative \\ Model\end{tabular}& Distance$^{\mathrm{a}}$ \\
  \hline
  Eiband~\cite{eiband2017understanding}  & Naked eye & $\times$ & $\times$ & 1m \\
  Kwon~\cite{kwon2013covert}  & Naked eye & $\times$ & $\times$ &-$^{\mathrm{b}}$\\
Schaub~\cite{schaub2012password} & Naked eye & \cmark & $\times$ & -\\
  Maggi~\cite{maggi2011poster}  & Camera & \cmark  & $\times$ &- \\
  \hline
  \hline
  \textbf{\textsf{SRPeek}} & COTS phones & \cmark & \cmark  & 1.8 / 6m\\
  \hline
  \multicolumn{5}{l}{$^{\mathrm{a}}$The maximum distance to the victim's screen. $^{\mathrm{b}}$The attacker stands}\\

  \multicolumn{5}{l}{next to the victim without the maximum effective distance.}\\
  \end{tabular}
  \label{tbl:comparison}
  \end{center}
\end{table}
